---
title: "Make map"
author: "DHJ"
date: "6 12 2019"
output: html_document
---

Making interactive map (using mapview) of marine stations (Økokyst and ocean acidification) as well as river/freshwater stations (RID and reference rivers)

## Packages

```{r}

library("niRvana")
library(dplyr)
library(purrr)
library(stringr)
library(ggplot2)

# NOTE:
# stations_from_project should add "project name" + coordinates, and remove ENTERED_BY, ENTERED_DATE
# And perhaps be able to handle >1 project at a time

# Set credentials, get projects
```

## Get projects

```{r}

## Set username + password for NIVAbase
# (Not needed if you have saved username + password for NIVAbase permanently using keyring )
# set_credentials()

df_projects <- get_projects()   # we call it 'df_projects' (the default name used by 'get_stations_from_project')

```

## RID stations   

### Select RID projects
```{r}
sel <- grepl("RID", df_projects$PROJECT_NAME)
# sum(sel)
df_projects[sel,]

```

### Stations
```{r}

# Get stations
# debugonce(get_stations_from_project)
df_stations_hoved <- get_stations_from_project("RID- Hovedelver", ignore.case = FALSE)  # PROJECT_ID 3320
df_stations_bi <- get_stations_from_project("RID - Bielver", ignore.case = FALSE)       # PROJECT_ID 3321

# Combine and add coordinates
RID_stations <- rbind(df_stations_hoved, df_stations_bi) %>%
  add_coordinates() %>%
  left_join(tibble(PROJECT_ID = c(3320, 3321), 
                   RID_type = c("RID hovedelver", "RID bielver")),
            by = "PROJECT_ID") %>%
  select(RID_type, everything())

```



### Data on map  

```{r}

ggplot(RID_stations, aes(LONGITUDE, LATITUDE, color = RID_type)) +
  geom_point()

```





## ØKOKYST, hydrography only    

* Not used, kept only for hiostorical reasons  

```{r}

okokyst_stations <- readxl::read_excel(
  "K:/Avdeling/214-Oseanografi/DATABASER/OKOKYST_2017/OKOKYST_Hydrografi_Stasjoner_v5.xlsx")

```

## ØKOKYST from NIVAbasen

```{r}

sel <- grepl("økokyst", df_projects$PROJECT_NAME, ignore.case = TRUE)
# sum(sel)
# df_projects[sel,]

# Stations from all recent ØKOKYST projects
prosj <- c("ØKOKYST Skagerrak 2017-2020",
           "ØKOKYST Nordsjøen Nord",
           "ØKOKYST Norskehavet Sør I",
           "ØKOKYST Norskehavet Sør II",
           "ØKOKYST Norskehavet Nord I",
           "ØKOKYST Barentshavet",
           "ØKOKYST Ferrybox")

# This adds a lot of data frames to the output:
df_stations <- prosj %>% 
  purrr::map_df(~get_stations_from_project(., ignore.case = FALSE, exact = TRUE))

OKOKYST_all_stations <- df_stations %>% 
  add_coordinates()

#
# This one is wrong - correct station added as extra data below (dat_xtra2)
#
sel <- OKOKYST_all_stations$STATION_CODE %in% "HT76"; sum(sel)
OKOKYST_all_stations <- OKOKYST_all_stations[!sel,]

# Save

if (FALSE) {
  openxlsx::write.xlsx(OKOKYST_all_stations, "Data/81_OKOKYST_all_stations.xlsx")
} 

```

### Projects and station codes  
```{r}
table(OKOKYST_all_stations$PROJECT_ID)  

# Types of statoins (see below)
table(substr(OKOKYST_all_stations$STATION_CODE, 1, 2))

# B = bløtbunn, H = hardbunn, V = Hydrografi
table(substr(OKOKYST_all_stations$STATION_CODE, 1, 1))

```

### Extra data 1
Gotten in mail from Camilla 5.12.2019, see text file in Input_data folder

```{r}
# Extra data (gotten in mail from Camilla 5.12.2019, see text file in Input_data folder)
dat_xtra1 <- readxl::read_excel("Input_data/Stasjoner Norskehavet Nord III.xlsx") %>%
  rename(STATION_CODE= `Stasjon #`, 
         STATION_NAME = `Stasjon navn`, 
         LONGITUDE = Longitude, LATITUDE = Latitude)

# Remove parantheses
dat_xtra1$STATION_CODE <- sub("(", "", dat_xtra1$STATION_CODE, fixed = TRUE)
dat_xtra1$STATION_CODE <- sub(")", "", dat_xtra1$STATION_CODE, fixed = TRUE)

table(substr(dat_xtra1$STATION_CODE, 1, 2))

```

### More extra data 
Gotten in mail from Camilla 9.12.2019, see text file in Input_data folder

```{r}
dat_xtra2 <- readxl::read_excel("Input_data/ØKOKYST stasjoner_ tillegg til kart.xlsx") %>%
  rename(STATION_CODE= `kode`, 
         STATION_NAME = `stasjonsnavn`, 
         LONGITUDE = long, LATITUDE = lat) %>%
  # The ones without parathesis and with 'opsjon' are deleted (they are double up)
  filter(!(substr(STATION_CODE,1,1) != "(" & `skal_utføres` == "opsjon"))

# Remove parantheses
dat_xtra2$STATION_CODE <- sub("(", "", dat_xtra2$STATION_CODE, fixed = TRUE)
dat_xtra2$STATION_CODE <- sub(")", "", dat_xtra2$STATION_CODE, fixed = TRUE)

# dat_xtra2

table(substr(dat_xtra2$STATION_CODE, 1, 2))


```

### Even more extra data 
Gotten in mail from Camilla 11.12.2019

```{r}

dat_xtra3 <- tibble(
  STATION_CODE = c("HT77", "HT78"), 
  STATION_NAME = c("Hemreviken", "Fuglbergøya"),
  LONGITUDE = c(14.83210, 14.68820), 
  LATITUDE = c(68.21070, 68.15380))


```

### Even more extra data, again 
Gotten in mail from Camilla 11.12.2019

```{r}

st <- c("HR19","HR121","HR153","HT28","HT27","HT33","HT34")

dat_xtra4 <- readxl::read_excel(
  "Input_data/Økokyststasjoner_tilbud2016_alle.xlsx",
  sheet = "hardbunn") %>% # names()
  rename(STATION_CODE = `St.nr`, 
         STATION_NAME = `St.navn`, 
         LONGITUDE = `...6`, LATITUDE = Posisjon) %>%
  filter(STATION_CODE %in% st) %>%
  select(STATION_NAME, STATION_CODE, LONGITUDE, LATITUDE)

```

### Add the 4 sets of extra data and add 'Stasjonstype' variable  
Note: G28 Gullholmen is a hard bottom station - I assume for trends.   
See "Årsrapport DP Skagerrak 2018.pdf" found in `K:\Prosjekter\Sjøvann\KYSTOVERVÅKING ØKOKYST\KYSTOVERVÅKING ØKOKYST 2017-2020\ØKOKYST DP Skagerrak O-17089_19089\Årsrapport2018\`  
```{r}

OKOKYST_all_stations2 <- bind_rows(
  OKOKYST_all_stations,
  dat_xtra1 %>% select(STATION_NAME, STATION_CODE, LONGITUDE, LATITUDE),
  dat_xtra2 %>% select(STATION_NAME, STATION_CODE, LONGITUDE, LATITUDE),
  dat_xtra3,
  dat_xtra4
  ) %>%
  mutate(Stasjonstype = case_when(substr(STATION_CODE,1,2) %in% "BT" ~ "Bløtbunn trend",
                             substr(STATION_CODE,1,2) %in% "BR" ~ "Bløtbunn referanse",
                             substr(STATION_CODE,1,2) %in% "VT" ~ "Hydrografi trend",
                             substr(STATION_CODE,1,2) %in% "VR" ~ "Hydrografi referanse",
                             substr(STATION_CODE,1,2) %in% "HT" ~ "Hardbunn trend",
                             STATION_CODE %in% "G28" ~ "Hardbunn trend",
                             substr(STATION_CODE,1,2) %in% c("HR","Hr") ~ "Hardbunn referanse",
                             substr(STATION_CODE,1,2) %in% "ZT" ~ "Ålegras trend",
                             substr(STATION_CODE,1,2) %in% "ZR" ~ "Ålegras referanse"
                             )
  )

if (FALSE)
  openxlsx::write.xlsx(OKOKYST_all_stations2, "Figures/01_01_Rid_and_Okokyst_coordinates.xlsx")

```


### Sort by position
```{r}

OKOKYST_all_stations2 <- OKOKYST_all_stations2 %>%
  mutate(LONGITUDE_plot1 = LONGITUDE,
         LATITUDE_plot1 = LATITUDE,
         LONGITUDE_plot2 = LONGITUDE,
         LATITUDE_plot2 = LATITUDE,
         LONGITUDE_plot3 = LONGITUDE,
         LATITUDE_plot3 = LATITUDE
         ) %>%
  arrange(LATITUDE, LONGITUDE, STATION_CODE)

```


### Remove duplicates  
```{r}
d_lat <- diff(OKOKYST_all_stations2$LATITUDE) == 0
d_lng <- diff(OKOKYST_all_stations2$LONGITUDE) == 0
d_code <- 
  head(OKOKYST_all_stations2$STATION_CODE, -1) == tail(OKOKYST_all_stations2$STATION_CODE, -1)

sum(d_lat & d_lng & d_code)

i_remove <- which(d_lat & d_lng & d_code)

# Remove
OKOKYST_all_stations2 <- OKOKYST_all_stations2[-i_remove,]
  
```


### Stations with same positions    
For making 3 versions:
-	Ver1: Stations with same coordinate moved 500 meter to South/North
-	Ver2: Stations with same coordinate moved 1000 meter to South/North
-	Ver3: Stations with same coordinate moved 2000 meter to South/North


```{r}

dist_move1 <- 0.5
dist_move2 <- 1
dist_move3 <- 0.25

d_lat <- diff(OKOKYST_all_stations2$LATITUDE) == 0
d_lng <- diff(OKOKYST_all_stations2$LONGITUDE) == 0

sum(d_lat & d_lng)

i1 <- which(d_lat & d_lng)
i2 <- sort(c(i1, i1+1))
i2

# Check
# OKOKYST_all_stations2[i2,] %>% 
#      select(STATION_NAME, STATION_CODE, LONGITUDE, LATITUDE, LATITUDE_plot2)

# Move all B (soft bottom) stations 500 m South, and all V stations 500 m North
# One latitude = 111.5 km
OKOKYST_all_stations2$LATITUDE_plot1[i1] <- 
  OKOKYST_all_stations2$LATITUDE[i1] - 1/111.5*dist_move1
OKOKYST_all_stations2$LATITUDE_plot1[i1+1] <- 
  OKOKYST_all_stations2$LATITUDE[i1+1] + 1/111.5*dist_move1

# same but longer
OKOKYST_all_stations2$LATITUDE_plot2[i1] <- 
  OKOKYST_all_stations2$LATITUDE[i1] - 1/111.5*dist_move2
OKOKYST_all_stations2$LATITUDE_plot2[i1+1] <- 
  OKOKYST_all_stations2$LATITUDE[i1+1] + 1/111.5*dist_move2

# Demonstrate (shown below)
OKOKYST_all_stations2[i2,] %>% 
     select(STATION_NAME, STATION_CODE, LONGITUDE, LATITUDE, LATITUDE_plot2)

# same but longer
OKOKYST_all_stations2$LATITUDE_plot3[i1] <- 
  OKOKYST_all_stations2$LATITUDE[i1] - 1/111.5*dist_move3
OKOKYST_all_stations2$LATITUDE_plot3[i1+1] <- 
  OKOKYST_all_stations2$LATITUDE[i1+1] + 1/111.5*dist_move3


```


### Stations with same positions, check
```{r}

library(nivamaps)
library(sf)
library(mapview)

make_point <- function(i, data, col_long, col_lat){
  data[i,c(col_long, col_lat)] %>% 
    as.numeric() %>%
    st_point()
}

df_test <- OKOKYST_all_stations2[i2,]

point_list <- 1:nrow(df_test) %>% 
  purrr::map(make_point, data = df_test, "LONGITUDE_plot2", "LATITUDE_plot2")
st_geometry(df_test) <- st_sfc(point_list, crs = 4326)

# RColorBrewer::display.brewer.all()
# RColorBrewer::display.brewer.pal(8, "Paired")
cols <- RColorBrewer::brewer.pal(10, "Paired") %>% rev()
cols <- cols[c(2,1,4,3,6,5,8,7,10,9)]

# Plot below
# mapview(df_test, zcol = "Stasjonstype", col.regions = cols, alpha.regions = 1) 

```

### Data on map  

```{r}

ggplot(OKOKYST_all_stations2, aes(LONGITUDE, LATITUDE, color = Stasjonstype)) +
  geom_point()

```


## Ocean acidification (havforsuring)  

```{r}

# STATION_NAME, Stasjonstype (= type stasjon), STATION_CODE, LONGITUDE, LATITUDE

oa_stations1 <- readxl::read_excel(
  "Input_data/Havforsuring 210044 Overview_saved4Jan2022.xlsx", 
  sheet = "Sampling overview", skip = 1
  ) %>%
  rename(
    STATION_NAME = Stasjon,
    STATION_CODE = `Stasjon nr.`,
    LATITUDE = `Latitude (decimal)`,
    LONGITUDE = `Longitude (decimal)`)

oa_stations <- oa_stations1 %>%
  filter(!is.na(LATITUDE)) %>%
  mutate(
    Stasjonstype = case_when(
      grepl("Kiel", STATION_NAME) ~ "OA Ferrybox",
      grepl("Tromsø", STATION_NAME) ~ "OA Ferrybox",
      `Instipro activity` %in% "KYST" ~ "OA Kyst",
      grepl("VT", STATION_CODE) ~ "OA Økokyst",
      grepl("VR", STATION_CODE) ~ "OA Økokyst",
      TRUE ~ "OA Kyst")
  )

table(oa_stations$Stasjonstype)

# oa_stations %>% select(Type:`Instipro activity`, Stasjonstype) %>% View()



```


### Data on map  

```{r}

ggplot(oa_stations, aes(LONGITUDE, LATITUDE, color = Stasjonstype)) +
  geom_point() 

```


## Reference rivers    

```{r}

#
# From Aquamonitor
#- not used - better to use excel file, which has information (directly) on chemical variables or not
#

if (FALSE){

  sel <- grepl("referanseelv", df_projects$PROJECT_NAME, ignore.case = TRUE)
  # sum(sel)
  df_projects[sel,]
  
  df_stations_referanseelv <- get_stations_from_project(
    "Overvåking av referanseelver", ignore.case = FALSE)  # PROJECT_ID 3320
  
}

reference_rivers_1 <- readxl::read_excel("Input_data/Referanseelver_stasjoner_per_2019.xlsx") 

table(addNA(reference_rivers_1$Fortsatt_med))
table(addNA(reference_rivers_1$Miljøgifter))

reference_rivers <- reference_rivers_1 %>%
  filter(Fortsatt_med == "ja") %>%
  rename(
    LONGITUDE = Lon,
    LATITUDE = Lat,
    STATION_CODE = Aquamonitor_stasjonskode) %>%
  mutate(
    STATION_NAME = stringr::str_sub(Rapportnavn, start = 5),
    Stasjonstype = case_when(
      `Miljøgifter` %in% "X" ~ "Ref. elver (med miljøgifter)",
      TRUE ~ "Ref. elver (uten miljøgifter)")
  )

```


### Data on map  

```{r}

ggplot(reference_rivers, aes(LONGITUDE, LATITUDE, color = Stasjonstype)) +
  geom_point()

```

## Combined ØKOKYST and RID stations   


### Combining  
Makes three sets of coordinates, as there will be made three sets of maps depending on how far same-coordinate stations are moved.

```{r}

# STATION_NAME first, for hover
df_comb <- bind_rows(
  RID_stations %>% 
    rename(Stasjonstype = RID_type) %>%
    mutate(LONGITUDE_plot1 = LONGITUDE,
           LATITUDE_plot1 = LATITUDE,
           LONGITUDE_plot2 = LONGITUDE,
           LATITUDE_plot2 = LATITUDE,
           LONGITUDE_plot3 = LONGITUDE,
           LATITUDE_plot3 = LATITUDE
    ),  
  oa_stations %>% 
    mutate(LONGITUDE_plot1 = LONGITUDE,
           LATITUDE_plot1 = LATITUDE,
           LONGITUDE_plot2 = LONGITUDE,
           LATITUDE_plot2 = LATITUDE,
           LONGITUDE_plot3 = LONGITUDE,
           LATITUDE_plot3 = LATITUDE
    ),  
  reference_rivers %>% 
    mutate(LONGITUDE_plot1 = LONGITUDE,
           LATITUDE_plot1 = LATITUDE,
           LONGITUDE_plot2 = LONGITUDE,
           LATITUDE_plot2 = LATITUDE,
           LONGITUDE_plot3 = LONGITUDE,
           LATITUDE_plot3 = LATITUDE
    ),  
  OKOKYST_all_stations2) %>% 
  select(STATION_NAME, Stasjonstype, STATION_CODE, 
         LONGITUDE, LATITUDE,
         LONGITUDE_plot1, LATITUDE_plot1,
         LONGITUDE_plot2, LATITUDE_plot2,
         LONGITUDE_plot3, LATITUDE_plot3
  )


```
### Test plot  
```{r}

ggplot(df_comb, aes(LONGITUDE_plot1, LATITUDE_plot1, color = Stasjonstype)) +
  geom_point()

```

## Interactive maps, source data  

### Makes three sets of data (for the three versions of maps)  
- With spatial column  

```{r}

# library(nivamaps)
library(sf)
library(mapview)

df_comb1 <- df_comb
df_comb2 <- df_comb
df_comb3 <- df_comb

make_point <- function(i, data, col_long, col_lat){
  data[i,c(col_long, col_lat)] %>% 
    as.numeric() %>%
    st_point()
}

point_list <- 1:nrow(df_comb) %>% 
  purrr::map(make_point, data = df_comb, "LONGITUDE_plot1", "LATITUDE_plot1")
st_geometry(df_comb1) <- st_sfc(point_list, crs = 4326)

point_list <- 1:nrow(df_comb) %>% 
  purrr::map(make_point, data = df_comb, "LONGITUDE_plot2", "LATITUDE_plot2")
st_geometry(df_comb2) <- st_sfc(point_list, crs = 4326)

point_list <- 1:nrow(df_comb) %>% 
  purrr::map(make_point, data = df_comb, "LONGITUDE_plot3", "LATITUDE_plot3")
st_geometry(df_comb3) <- st_sfc(point_list, crs = 4326)


# RColorBrewer::display.brewer.all()
# RColorBrewer::display.brewer.pal(8, "Paired")
cols <- RColorBrewer::brewer.pal(10, "Paired") %>% rev()
cols <- cols[c(2,1,4,3,6,5,8,7,10,9)]

#
# Labels for mouseover
#
label_1 <- with(df_comb1, paste0(STATION_CODE, " (", STATION_NAME, ")"))
label_2 <- with(df_comb2, paste0(STATION_CODE, " (", STATION_NAME, ")"))
label_3 <- with(df_comb3, paste0(STATION_CODE, " (", STATION_NAME, ")"))

```

## Interactive maps 1

### Interactive plot (variant 2)  

```{r}

# Plot below
mapview(df_comb2, zcol = "Stasjonstype", col.regions = cols, alpha.regions = 1,
        label = label_2)


```

### Save interactive maps  
6 versions:  
  - 3 versions (depending of movement of same-coordinate stations) * 2 point-size verions

```{r}
# df_comb_data <- df_comb[c("STATION_CODE", "Stasjonstype")] %>% as.data.frame()


# Original point size
mapview(df_comb1, zcol = "Stasjonstype", 
        col.regions = cols, alpha.regions = 1,
        label = label_1
        ) %>%
  mapshot("Figures/01_Rid_and_Okokyst_ver1.html")

# With smaller dots, for showng all or Norway
mapview(df_comb1, zcol = "Stasjonstype", 
        col.regions = cols, alpha.regions = 1, 
        label = label_1, cex = 3) %>%
  mapshot("Figures/01_Rid_and Okokyst_small_ver1.html")


# Static plots
mapview(df_comb2, zcol = "Stasjonstype", 
        col.regions = cols, alpha.regions = 1,
        label = label_2
        ) %>%
  mapshot("Figures/01_Rid_and_Okokyst_ver2.html")

# With smaller dots, for showng all or Norway
mapview(df_comb2, zcol = "Stasjonstype", 
        col.regions = cols, alpha.regions = 1, 
        label = label_2, cex = 3) %>%
  mapshot("Figures/01_Rid_and Okokyst_small_ver2.html")


# Static plots
mapview(df_comb3, zcol = "Stasjonstype", 
        col.regions = cols, alpha.regions = 1,
        label = label_3
        ) %>%
  mapshot("Figures/01_Rid_and_Okokyst_ver3.html")

# With smaller dots, for showng all or Norway
mapview(df_comb3, zcol = "Stasjonstype", 
        col.regions = cols, alpha.regions = 1, 
        label = label_3, cex = 3) %>%
  mapshot("Figures/01_Rid_and Okokyst_small_ver3.html")


# nivamaps  
# make_map(62, 10, zoom = 6) %>%
#   add_points(df_sel2[,c(2,1,3)], radius = 5, col_popup = 3) %>% 
#   make_html(filename = "Figures/Rid_and Okokyst_interactive.html") 
#rstudioapi::viewer("test.html")

# nivamaps::add_points()

```

## Interactive maps 2 (ver 4)   
- HTML files version 4a and 4b  

### Separate data for each station type     
```{r}

#
# Better; Split by first part of 'Stasjonstype' (Bløtbunn, hardbunn etc) => 5 layers  
#

table(df_comb2$Stasjonstype)  

df_comb2_ver4 <- df_comb2 %>%
  select(
    -c(LONGITUDE_plot1, LONGITUDE_plot2, LONGITUDE_plot3, 
       LATITUDE_plot1, LATITUDE_plot2, LATITUDE_plot3)) %>%
  mutate(
    Type = case_when(
      grepl("Ref. elver", Stasjonstype) ~ "Referanseelver",
      grepl("OA", Stasjonstype) ~ "Havforsuring",
      TRUE ~ Stasjonstype %>% stringr::str_extract("[^[[:blank:]]]+")
      ),
    Type = case_when(
      Type %in% c("Bløtbunn", "Hardbunn", "Hydrografi", "Ålegras") ~ paste("Økokyst -", Type), 
      Type %in% "RID" ~ "RID-elver", 
      TRUE ~ Type),
    Type = factor(Type, levels = c("Økokyst - Bløtbunn", "Økokyst - Hardbunn", 
                                   "Økokyst - Hydrografi", "Økokyst - Ålegras", 
                                   "Havforsuring", "RID-elver", "Referanseelver")),
    Label = paste0(STATION_CODE, " (", STATION_NAME, ")")   # for mouseover
  )

# names(table(df_comb2_ver4$Type)) %>% dput()

# Check
# df_comb2_ver4 %>% count(Type, Stasjonstype) %>% View()
table(df_comb2_ver4$Type)  
# table(df_comb2_ver4$Stasjonstype, df_comb2_ver4$Type)  

#
# Make list
#
df_comb2_ver4_list <- df_comb2_ver4 %>%
  base::split(df_comb2_ver4$Type)

df_comb2_ver4_list %>% map_int(nrow)

```

### Colors 

```{r}

# Colors
# RColorBrewer::display.brewer.all()

# Qualitative color schemes by Paul Tol
#     https://www.r-bloggers.com/the-paul-tol-21-color-salute/
#     http://www.sron.nl/~pault/colourschemes.pdf
#     Paul Tol 2012. Colour Schemes. SRON Technical Note SRON/EPS/TN/09-002 (issue 2.2)

if (FALSE){
  
# tol15rainbow
cols <- c("#114477", "#4477AA", "#77AADD", "#117755", "#44AA88", "#99CCBB", "#777711", "#AAAA44", "#DDDD77", "#771111", "#AA4444", "#DD7777", "#771144", "#AA4477", "#DD77AA")
pie(rep(1,length(cols)), col = cols)

# tol7qualitative
cols <- c("#332288", "#88CCEE", "#44AA99", "#117733", "#DDCC77", "#CC6677","#AA4499")
pie(rep(1,length(cols)), col = cols)

# tol10qualitative
tol10qualitative=c("#332288", "#88CCEE", "#44AA99", "#117733", "#999933", "#DDCC77", "#661100", "#CC6677", "#882255", "#AA4499")
pie(rep(1,length(cols)), col = cols)

}

# tol21rainbow
# Then just use some of tjem
cols <-  c("#771155", "#AA4488", "#CC99BB", "#114477", "#4477AA", "#77AADD", "#117777", "#44AAAA", "#77CCCC", "#117744", "#44AA77", "#88CCAA", "#777711", "#AAAA44", "#DDDD77", "#774411", "#AA7744", "#DDAA77", "#771122", "#AA4455", "#DD7788")
pie(rep(1,length(cols)), col = cols)
# These two are a bit similar to no. 7 and 8, so we change them manually:
cols[10] <- "limegreen"
cols[11] <- "lawngreen"
pie(rep(1,length(cols)), col = cols)

# NOte: element 5 (IO stations) have 3 levels
col_list <- list(cols[1:2], cols[4:5], cols[7:8], cols[10:11], cols[13:15], cols[16:17], cols[19:20])


```

### Make interactive map a  
Original point size  
```{r}


map_list <- seq_along(df_comb2_ver4_list) %>%
  purrr::map(
    ~mapview(df_comb2_ver4_list[[.x]], 
             zcol = "Stasjonstype", 
             col.regions = col_list[[.x]], 
             alpha.regions = 1,
             label = df_comb2_ver4_list[[.x]]$Label, 
             layer.name = names(df_comb2_ver4_list)[.x])
)

final_map_ver4a <- map_list[[1]]
for (i in 2:length(map_list))
  final_map_ver4a <- final_map_ver4a + map_list[[i]]

```



### Make interactive map b  
Smaller point size  
```{r}

map_list <- seq_along(df_comb2_ver4_list) %>%
  purrr::map(
    ~mapview(df_comb2_ver4_list[[.x]], 
             zcol = "Stasjonstype", 
             col.regions = col_list[[.x]], 
             alpha.regions = 1,
             label = df_comb2_ver4_list[[.x]]$Label, 
             layer.name = names(df_comb2_ver4_list)[.x],
             cex = 3)
)


final_map_ver4b <- map_list[[1]]
for (i in 2:length(map_list))
  final_map_ver4b <- final_map_ver4b + map_list[[i]]

```


### Save   
- Also save do
```{r} 

fn <- "01_Rid_and_Okokyst_ver4a.html"
final_map_ver4a %>% mapshot(paste0("Figures/", fn))
final_map_ver4a %>% mapshot(paste0("K:/Avdeling/214-Oseanografi/DHJ/Data/Maps/Økokyst-kart/", fn))

fn <- "01_Rid_and_Okokyst_ver4b.html"
final_map_ver4b %>% mapshot(paste0("Figures/", fn))
final_map_ver4b %>% mapshot(paste0("K:/Avdeling/214-Oseanografi/DHJ/Data/Maps/Økokyst-kart/", fn))

# This doesn't work (we need to do it in windows, as there are a bunch of extra :
# file.copy(
#   paste0("Figures/", fn),
#   paste0("K:/Avdeling/214-Oseanografi/DHJ/Data/Maps/Økokyst-kart/", fn)
# )

# Note: also put on Google docs
# 

```


## Interactive maps 3 (ver 5)   

- HTML files version 5a and 5b  
- Økokyst in a single group (Type)   
- NOTE: mouseover text doesn't fit with station (although variable "Label" is correct.) 

### Separate data    
- 
```{r}

#
# Better; Split by first part of 'Stasjonstype' (Bløtbunn, hardbunn etc) => 5 layers  
#

table(df_comb2$Stasjonstype)  

df_comb2_ver5 <- df_comb2 %>%
  mutate(
    Type = case_when(
      grepl("Ref. elver", Stasjonstype) ~ "Referanseelver",
      grepl("OA", Stasjonstype) ~ "Havforsuring",
      TRUE ~ Stasjonstype %>% stringr::str_extract("[^[[:blank:]]]+")
      ),
    Type = case_when(
      Type %in% c("Bløtbunn", "Hardbunn", "Hydrografi", "Ålegras") ~ "Økokyst",   # CHANGED
      Type %in% "RID" ~ "RID-elver", 
      TRUE ~ Type),
    Type = factor(Type, levels = c("Økokyst",                                     # CHANGED 
                                   "Havforsuring", "RID-elver", "Referanseelver")),
    Label = paste0(STATION_CODE, " (", STATION_NAME, ")")   # for mouseover
  )

# names(table(df_comb2_ver5$Type)) %>% dput()

# Check
# df_comb2_ver5 %>% count(Type, Stasjonstype) %>% View()
# table(df_comb2_ver5$Type)  
# table(df_comb2_ver5$Stasjonstype, df_comb2_ver5$Type)  

#
# Make list
#
df_comb2_ver5_list <- df_comb2_ver5 %>%
  base::split(df_comb2_ver5$Type)

df_comb2_ver5_list %>% map_int(nrow)

```


### Colors 

```{r}

# NOte: element 5 (IO stations) have 3 levels
col_list_b <- list(cols[c(1:2, 4:5, 7:8, 10:11)], cols[13:15], cols[16:17], cols[19:20])


```

### Make interactive map a  
Original point size  
```{r}


map_list <- seq_along(df_comb2_ver5_list) %>%
  purrr::map(
    ~mapview(df_comb2_ver5_list[[.x]], 
             zcol = "Stasjonstype", 
             col.regions = col_list_b[[.x]], 
             alpha.regions = 1,
             label = df_comb2_ver5_list[[.x]]$Label, 
             layer.name = names(df_comb2_ver5_list)[.x])
)

final_map_ver5a <- map_list[[1]]
for (i in 2:length(map_list))
  final_map_ver5a <- final_map_ver5a + map_list[[i]]

```



### Make interactive map b  
Smaller point size  
```{r}

map_list <- seq_along(df_comb2_ver5_list) %>%
  purrr::map(
    ~mapview(df_comb2_ver5_list[[.x]], 
             zcol = "Stasjonstype", 
             col.regions = col_list_b[[.x]], 
             alpha.regions = 1,
             label = df_comb2_ver5_list[[.x]]$Label, 
             layer.name = names(df_comb2_ver5_list)[.x],
             cex = 3)
)

final_map_ver5b <- map_list[[1]]
for (i in 2:length(map_list))
  final_map_ver5b <- final_map_ver5b + map_list[[i]]

```


### Save
```{r} 

fn <- "01_Rid_and_Okokyst_ver5a.html"
final_map_ver5a %>% mapshot(paste0("Figures/", fn))
final_map_ver5a %>% mapshot(paste0("K:/Avdeling/214-Oseanografi/DHJ/Data/Maps/Økokyst-kart/", fn))

fn <- "01_Rid_and_Okokyst_ver5b.html"
final_map_ver5b %>% mapshot(paste0("Figures/", fn))
final_map_ver5b %>% mapshot(paste0("K:/Avdeling/214-Oseanografi/DHJ/Data/Maps/Økokyst-kart/", fn))

```
