---
title: "Make map"
author: "DHJ"
date: "6 12 2019"
output: html_document
---


```{r}

library("niRvana")
library(dplyr)
library(ggplot2)

# NOTE:
# stations_from_project should add "project name" + coordinates, and remove ENTERED_BY, ENTERED_DATE
# And perhaps be able to handle >1 project at a time

# Set credentials, get projects
```


## Enter uesename + passwrd for NIVAbase  
```{r}
set_credentials()

```

## Data


### Get projects

```{r}

df_projects <- get_projects()   # we call it 'df_projects' (the default name used by 'get_stations_from_project')

```

### RID stations   

#### Select RID projects
```{r}
sel <- grepl("RID", df_projects$PROJECT_NAME)
# sum(sel)
df_projects[sel,]

```

#### Stations
```{r}
# Get stations
df_stations_hoved <- get_stations_from_project("RID- Hovedelver", ignore.case = FALSE)  # PROJECT_ID 3320
df_stations_bi <- get_stations_from_project("RID - Bielver", ignore.case = FALSE)       # PROJECT_ID 3321
df_stations <- rbind(df_stations_hoved, df_stations_bi)

# Add info from table STATIONS
df_stations2 <- get_nivabase_selection("*", "STATIONS", "STATION_ID", df_stations$STATION_ID)
df_stations <- df_stations %>% 
  left_join(df_stations2 %>% select(STATION_ID, GEOM_TYPE_ID, GEOM_REF_ID, STATION_TYPE_ID),
            by = "STATION_ID")

# Get coordinates  
df_positions <- get_nivabase_selection(
  "LONGITUDE, LATITUDE, SAMPLE_POINT_ID", 
  "SAMPLE_POINTS", 
  "SAMPLE_POINT_ID", df_stations$GEOM_REF_ID, owner = "NIVA_GEOMETRY"
)

# Add coordinates from table SAMPLE_POINTS
df_stations <- df_stations %>% 
  left_join(df_positions, by = c("GEOM_REF_ID" = "SAMPLE_POINT_ID"))

# coor to numeric
for (col in c("LONGITUDE", "LATITUDE"))
  df_stations[[col]] <- sub(",", ".", df_stations[[col]]) %>% as.numeric()

df_stations <- df_stations %>%
  left_join(tibble(PROJECT_ID = c(3320, 3321), RID_type = c("RID hovedelver", "RID bielver")),
            by = "PROJECT_ID")

```

#### Map

```{r}
ggplot(df_stations, aes(LONGITUDE, LATITUDE, color = RID_type)) +
  geom_point()

```

#### Final data

```{r}

RID_stations <- df_stations %>% 
  select(-c(ENTERED_BY, ENTERED_DATE, GEOM_TYPE_ID, GEOM_REF_ID)) %>%
  select(RID_type, everything())

```

### ØKOKYST, hydrography only   

#### Data   
```{r}

okokyst_stations <- readxl::read_excel("K:/Avdeling/214-Oseanografi/DATABASER/OKOKYST_2017/OKOKYST_Hydrografi_Stasjoner_v5.xlsx")


df_comb <- bind_rows(RID_stations %>% rename(Stasjon = RID_type),
                     tibble(Stasjon = "ØKOKYST", 
                            LONGITUDE = okokyst_stations$Longitude,
                            LATITUDE = okokyst_stations$Latitude
                            )
                     )

```

## Map

```{r}
ggplot(df_comb, aes(LONGITUDE, LATITUDE, color = Stasjon)) +
  geom_point()

```

## ØKOKYST from NIVAbasen

```{r}

sel <- grepl("økokyst", df_projects$PROJECT_NAME, ignore.case = TRUE)
# sum(sel)
# df_projects[sel,]

# Stations from all recent ØKOKYST projects
prosj <- c("ØKOKYST Skagerrak 2017-2020",
           "ØKOKYST Nordsjøen Nord",
           "ØKOKYST Norskehavet Sør I",
           "ØKOKYST Norskehavet Sør II",
           "ØKOKYST Norskehavet Nord I",
           "ØKOKYST Barentshavet",
           "ØKOKYST Ferrybox")

# This adds a lot of data frames to the output:
df_stations <- prosj %>% 
  purrr::map_df(~get_stations_from_project(., ignore.case = FALSE, exact = TRUE))

# Add 'GEOM_REF_ID' from table STATIONS
df_stations2 <- get_nivabase_selection("*", "STATIONS", "STATION_ID", df_stations$STATION_ID)
df_stations <- df_stations %>% 
  left_join(df_stations2 %>% select(STATION_ID, GEOM_REF_ID),
            by = "STATION_ID")

# Get coordinates
df_positions <- get_nivabase_selection(
  "LONGITUDE, LATITUDE, SAMPLE_POINT_ID", 
  "SAMPLE_POINTS", 
  "SAMPLE_POINT_ID", df_stations$GEOM_REF_ID, owner = "NIVA_GEOMETRY"
)


# Add coordinates from table SAMPLE_POINTS
df_stations <- df_stations %>% 
  left_join(df_positions, by = c("GEOM_REF_ID" = "SAMPLE_POINT_ID"))

# coor to numeric
for (col in c("LONGITUDE", "LATITUDE"))
  df_stations[[col]] <- sub(",", ".", df_stations[[col]]) %>% as.numeric()

# Remove unnecessary columns
OKOKYST_all_stations <- df_stations %>% 
  select(-c(ENTERED_BY, ENTERED_DATE)) %>%
  select(everything())

# Save

if (FALSE) {
  openxlsx::write.xlsx(OKOKYST_all_stations, "Data/81_OKOKYST_all_stations.xlsx")
} 

```

### Projects and station codes  
```{r}
table(OKOKYST_all_stations$PROJECT_ID)  

# Types of statoins (see below)
table(substr(OKOKYST_all_stations$STATION_CODE, 1, 2))

# B = bløtbunn, H = hardbunn, V = Hydrografi
table(substr(OKOKYST_all_stations$STATION_CODE, 1, 1))

```

### Extra data 
Gotten in mail from Camilla 5.12.2019, see text file in Input_data folder

```{r}
# Extra data (gotten in mail from Camilla 5.12.2019, see text file in Input_data folder)
dat_xtra <- readxl::read_excel("Input_data/Stasjoner Norskehavet Nord III.xlsx") %>%
  rename(STATION_CODE= `Stasjon #`, 
         STATION_NAME = `Stasjon navn`, 
         LONGITUDE = Longitude, LATITUDE = Latitude)

# Remove parantheses
dat_xtra$STATION_CODE <- sub("(", "", dat_xtra$STATION_CODE, fixed = TRUE)
dat_xtra$STATION_CODE <- sub(")", "", dat_xtra$STATION_CODE, fixed = TRUE)

table(substr(dat_xtra$STATION_CODE, 1, 2))

```

### More extra data 
Gotten in mail from Camilla 9.12.2019, see text file in Input_data folder

```{r}
dat_xtra2 <- readxl::read_excel("Input_data/ØKOKYST stasjoner_ tillegg til kart.xlsx") %>%
  rename(STATION_CODE= `kode`, 
         STATION_NAME = `stasjonsnavn`, 
         LONGITUDE = long, LATITUDE = lat) %>%
  # The ones without parathesis and with 'opsjon' are deleted (they are double up)
  filter(!(substr(STATION_CODE,1,1) != "(" & `skal_utføres` == "opsjon"))

# Remove parantheses
dat_xtra2$STATION_CODE <- sub("(", "", dat_xtra2$STATION_CODE, fixed = TRUE)
dat_xtra2$STATION_CODE <- sub(")", "", dat_xtra2$STATION_CODE, fixed = TRUE)

# dat_xtra2

table(substr(dat_xtra2$STATION_CODE, 1, 2))


```

### Add extra data and add 'Stasjon' variable  
Note: G28 Gullholmen is a hard bottom station - I assume for trends.   
See "Årsrapport DP Skagerrak 2018.pdf" found in `K:\Prosjekter\Sjøvann\KYSTOVERVÅKING ØKOKYST\KYSTOVERVÅKING ØKOKYST 2017-2020\ØKOKYST DP Skagerrak O-17089_19089\Årsrapport2018\`  
```{r}

OKOKYST_all_stations2 <- bind_rows(
  OKOKYST_all_stations,
  dat_xtra %>% select(STATION_NAME, STATION_CODE, LONGITUDE, LATITUDE),
  dat_xtra2 %>% select(STATION_NAME, STATION_CODE, LONGITUDE, LATITUDE)
  ) %>%
  mutate(Stasjon = case_when(substr(STATION_CODE,1,2) %in% "BT" ~ "Bløtbunn trend",
                             substr(STATION_CODE,1,2) %in% "BR" ~ "Bløtbunn referanse",
                             substr(STATION_CODE,1,2) %in% "VT" ~ "Hydrografi trend",
                             substr(STATION_CODE,1,2) %in% "VR" ~ "Hydrografi referanse",
                             substr(STATION_CODE,1,2) %in% "HT" ~ "Hardbunn trend",
                             STATION_CODE %in% "G28" ~ "Hardbunn trend",
                             substr(STATION_CODE,1,2) %in% c("HR","Hr") ~ "Hardbunn referanse",
                             substr(STATION_CODE,1,2) %in% "ZT" ~ "Ålegras trend",
                             substr(STATION_CODE,1,2) %in% "ZR" ~ "Ålegras referanse"
                             )
  )

openxlsx::write.xlsx(OKOKYST_all_stations2, "Figures/01_01_Rid_and_Okokyst_coordinates.xlsx")

```



## Combined ØKOKYST and RID stations 

```{r}

# STATION_NAME first, for hover
df_comb <- bind_rows(RID_stations %>% 
                       rename(Stasjon = RID_type) %>%
                       select(STATION_NAME, Stasjon, STATION_CODE, LONGITUDE, LATITUDE),  
                     OKOKYST_all_stations2 %>% 
                       select(STATION_NAME, Stasjon, STATION_CODE, LONGITUDE, LATITUDE)
)

ggplot(df_comb, aes(LONGITUDE, LATITUDE, color = Stasjon)) +
  geom_point()

```

### Make interactive map

```{r}

library(nivamaps)
library(sf)
library(mapview)


make_point <- function(i, data, col_long, col_lat){
  data[i,c(col_long, col_lat)] %>% 
    as.numeric() %>%
    st_point()
}

point_list <- 1:nrow(df_comb) %>% purrr::map(make_point, data = df_comb, "LONGITUDE", "LATITUDE")
st_geometry(df_comb) <- st_sfc(point_list, crs = 4326)

# RColorBrewer::display.brewer.all()
# RColorBrewer::display.brewer.pal(8, "Paired")
cols <- RColorBrewer::brewer.pal(10, "Paired") %>% rev()
cols <- cols[c(2,1,4,3,6,5,8,7,10,9)]

# Plot below
mapview(df_comb, zcol = "Stasjon", col.regions = cols, alpha.regions = 1) 

```

```{r}
# df_comb_data <- df_comb[c("STATION_CODE", "Stasjon")] %>% as.data.frame()

# Static plots
mapview(df_comb, zcol = "Stasjon", 
        col.regions = cols, alpha.regions = 1
        ) %>%
  mapshot("Figures/01_Rid_and_Okokyst.html")

# With smaller dots, for showng all or Norway
mapview(df_comb, zcol = "Stasjon", col.regions = cols, alpha.regions = 1, cex = 3) %>%
  mapshot("Figures/01_Rid_and Okokyst_small.html")

# nivamaps  
# make_map(62, 10, zoom = 6) %>%
#   add_points(df_sel2[,c(2,1,3)], radius = 5, col_popup = 3) %>% 
#   make_html(filename = "Figures/Rid_and Okokyst_interactive.html") 
#rstudioapi::viewer("test.html")

# nivamaps::add_points()

```
```{r}
df_comb_data <- df_comb[c("STATION_CODE", "Stasjon")] %>% as.data.frame()

mapview(df_comb, zcol = "Stasjon", 
        col.regions = cols, alpha.regions = 1
        )

```

